### 2019-12-14 README.Rmd
rearranging package

# sfzoner

@@

The goal of sfzoner is to ...

@@

You can install the released version of sfzoner from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sfzoner")
```

@@

``` r
# install.packages("devtools")
devtools::install_github("robinlovelace/sfzoner")
```

@@

```{r}
library(sf)
devtools::load_all()
plot(sz_region)
```

@@

```{r}
x = sz_region
q = sz_quadrat(x, 4) # break into 4
plot(q)
```

@@

```{r}
plot(sz_doughnut(x, n = 4))
doughnut_4km = sz_doughnut(x, d = 4)
doughnut_4km
plot(sf::st_geometry(doughnut_4km))
plot(doughnut_4km[3, ], col = "blue", add = TRUE)
```

>>>>

# zonebuilder

@@

The goal of zonebuilder is to ...

@@

You can install the released version of zonebuilder from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("zonebuilder")
```

@@

``` r
# install.packages("devtools")
devtools::install_github("robinlovelace/zonebuilder")
```

@@

```{r}
library(sf)
devtools::load_all()
plot(zb_region)
```

@@

```{r}
x = zb_region
q = zb_quadrat(x, 4) # break into 4
plot(q)
```

@@

```{r}
plot(zb_doughnut(x, n = 4))
doughnut_4km = zb_doughnut(x, d = 4)
doughnut_4km
plot(sf::st_geometry(doughnut_4km))
plot(doughnut_4km[3, ], col = "blue", add = TRUE)
```
